

\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{red}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding 
\usepackage[scale=0.75]{geometry}


% personal data
\name{Umut}{Seven}
\title{Curriculum Vit\ae}                               % optional, remove / comment the line if not wanted
\address{Bristol, UK}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+44~(736)~682~3919}                   % optional, remove / comment the line if not wanted
\email{umutseven92@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{umutseven.com} 
\github{github.com/umutseven92}  
\extrainfo{linkedin.com/in/umut-seven-03a459107/}  


\begin{document}

\makecvtitle

\section{Summary}
\vspace{5px}

Full Stack Software Engineer with a knack for telecommunications, blockchain \& information security, with an M.S. in Software Engineering from Boğaziçi University.
\vspace{5px}

My experience lies in building software products that are secure \& scalable. I have worked on all parts of said products, from back-end Microservices to Mobile Apps and Web Interfaces (UI).

\vspace{5px}

\textbf{Proficient in: }C\#, .NET, ASP.NET MVC, Java, Spring, Flutter, Dart, Python, Django, Blockchain, Firebase.\newline
\textbf{Competent in: }Javascript, Angular, Kotlin, C, C++, F\#, Prolog, SQL, HTML, CSS, AWS.

\vspace{5px}

\section{Professional Experience}

\cventry{Mar 2019-- Currently Employed}{Mobile Engineer - Flutter, Dart}{Cookpad}{Bristol, UK}{}{Development of both Android and iOS apps using Flutter \& Dart, using the full spectrum of Firebase tools like Cloud Firestore, Firebase Cloud Messaging and Firebase Cloud Functions. \newline{}} 
\vspace{5px}

\cventry{Sep 2018-- Feb 2019}{Software Developer - Java}{4Play Digital Workshop}{Istanbul, Turkey}{}{Development of web services and miscellaneous VAS services for mobile operators. Designing the software development process and implementing agile methodologies for the development team. \newline{}} 
\vspace{5px}

\cventry{Feb 2018-- Aug 2018}{Software Developer - C\#, JavaScript}{Armut.com}{Istanbul, Turkey}{}{Development of both the front-end and the back-end services of armut.com, leveraging multiple AWS products to deploy and monitor services. Implementing the CI/CD pipeline of multiple microservices. \newline{}} 
\vspace{5px}

\cventry{Sep 2015--Feb 2018}{Software Developer - C\#, JavaScript}{P.I. Works}{Istanbul, Turkey}{}{Development of multiple real-time software projects that optimize \& profile base stations, making the mobile operators more efficient and less error prone. Design and development of customized DevOps tools. \newline{}} 
\vspace{5px}

\cventry{Jul 2014--Sep 2014}{Software Development Intern - C\#, JavaScript, Python}{P.I. Works}{Istanbul, Turkey}{}{Development of web \& desktop based performance monitoring and reporting tools. Improving the CI/CD process. \newline{}} 
\vspace{5px}

\cventry{Jul 2013--Aug 2013}{Software Development Intern - C\#}{Borusan Oto}{Istanbul, Turkey}{}{Development of in-house CRM software. Improving communication between automobile parts dealers and existing customers. \newline{}} 
\vspace{5px}

\section{Education}
\vspace{5px}

\cventry{2017--2019}{Software Engineering}{Boğaziçi University}{Istanbul, Turkey}{\textit{MS}}{}  % arguments 3 to 6 can be left empty
\vspace{5px}
\cventry{2010--2015}{Business Administration}{Istanbul University}{Istanbul, Turkey}{\textit{BA}}{}  % arguments 3 to 6 can be left empty
\vspace{5px}

\section{Personal Projects}
\vspace{5px}
\cventry{}{Python}{LaFontaine}{}{}{
LaFontaine is an automatic movie trailer generator. LaFontaine creates movie trailers for any genre using pre-defined features, like number of faces on screen, and loudness of volume. Scenes are extracted using these features and combined to create the final trailer. There are three features for frame, three features for sound and three features for subtitles. Features are read from configurations and are fully configurable.
 \newline{}%
Links:%
\begin{itemize}%
\item \url{https://github.com/umutseven92/LaFontaine}\newline{}
\end{itemize}}

\vspace{5px}
\cventry{}{Python, Django}{Sentweet}{}{}{
Sentweet is a sentiment analyzer \& visualizer that uses the Twitter API. It allows users to perform sentiment analysis via a web user interface. It queries the Twitter API and charts out the general feelings people have about a certain topic. This project was built for Boğaziçi University Software Engineering Masters Programme, under the supervision of Prof. Dr. Suzan Üsküdarli. \newline{}%
Links:%
\begin{itemize}%
\item \url{https://github.com/umutseven92/Sentweet}\newline{}
\end{itemize}}
\vspace{5px}

\cventry{}{C\#, ASP.NET Core}{Plutus}{}{}{Plutus is a customizable, exchange agnostic cryptocurrency trading bot. You configure which cryptocurrencies to buy \& sell, your desired profit amount \& loss tolerance, and which cryptocurrency exchanges you want to buy \& sell from. It does the rest by predicting if the price is going up or down for a given coin and buying and selling according to your profit and loss stops. \newline{}%
Links:%
\begin{itemize}%
\item \url{https://github.com/umutseven92/Plutus}\newline{}
\end{itemize}}
\vspace{5px}
\newpage
\cventry{}{C\#, .NET Core}{SharpChain}{}{}{SharpChain is a simple blockchain implementation for educational purposes, written in C\#. It is a simpler, smaller model of the Bitcoin blockchain. I believe it makes it easier to see how the blockchain actually works nicely. \newline{}%
Links:%
\begin{itemize}%
\item \url{https://github.com/umutseven92/SharpChain}\newline{}
\end{itemize}}
\vspace{5px}

\color{color2} \centerline {\{ To see all my projects, please check out my GitHub profile @ github.com/umutseven92 \}}
\color{color3}

\vspace{5px}


\section{Certifications \& Training}
\vspace{5px}

\textbf{Qualifications}
\begin{itemize}
\item Microsoft Certified Professional (MC ID: 10495811)
\item TÜBİTAK 2014 Software Competition Finalist\newline{}
\end{itemize}
\textbf{Certificates}
\begin{itemize}
\item Microsoft Certified Professional Certificate (E498-2569)
\item Programming in C\# Specialist Certificate (E498-2567)
\item Bilge Adam MCSD Certificate of Excellence
\item Bilge Adam MCSD Participation\newline{}
\end{itemize}

\textbf{Trainings}
\begin{itemize}
\item MCSD Training in Bilge Adam\newline{}
\end{itemize}

\vspace{5px}


\section{Miscellaneous}
\vspace{5px}

\cvitemwithcomment{Hobbies}{Squash, Playing Guitar, Playing Piano}{}
\cvitemwithcomment{Other}{Fluent in English (IELTS Score of 8.5)}{}

               
\vspace*{\fill}
\color{color2} \centerline{\{ The source code for this CV can be found at https://github.com/umutseven92/UmutSevenCV \}}
\end{document}
